### 2009-03-26 doc/storage_system/arc-storage-manual.tex
some small (last) updates

\begin{verbatim}
$ arc_storage_cli mkdir /
- Calling the Bartender's makeCollection method...
- done in 0.81 seconds.
Creating collection '/': done

@@

\begin{verbatim}
$ arc_storage_cli mkdir /fruits
- Calling the Bartender's makeCollection method...
- done in 0.79 seconds.
Creating collection '/fruits': done

$ arc_storage_cli mkdir /fruits/apple
- Calling the Bartender's makeCollection method...
- done in 0.91 seconds.
Creating collection '/fruits/apple': done

@@

$ arc_storage_cli mkdir /
- Calling the Bartender's makeCollection method...
- done in 0.63 seconds.
Creating collection '/': done

@@

With only one node of the replicated A-Hash the system is not ready to work, if we try to use it, we get an error message:
\begin{verbatim}
$ arc_storage_cli mkdir /
- Calling the Bartender's makeCollection method...
- done in 0.55 seconds.
Creating collection '/': failed to create new librarian entry
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli mkdir /
- Calling the Bartender's makeCollection method...
- done in 1.16 seconds.
Creating collection '/': done
$ arc_storage_cli put orange /
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0214 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 2.22 seconds.
- Got transfer URL: http://storage:60001/hopi/3f903c50-0424-2891-5730-521cc00d96dc
- Uploading from 'orange'
    to 'http://storage:60001/hopi/3f903c50-0424-2891-5730-521cc00d96dc' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0293 seconds.
'orange' (7 bytes) uploaded as '/orange'.
$ arc_storage_cli modify /orange set states neededReplicas 3
- Calling the Bartender's modify method...
- done in 0.74 seconds.
set
$ arc_storage_cli stat /orange
[...]
  locations
    https://storage:60000/Shepherd f4ad8530-354d-5066-04ae-c54c94fd525b: alive
[...]
zsombor@storage:~$ arc_storage_cli stat /orange
[...]
  locations
    https://storage:60000/Shepherd f4ad8530-354d-5066-04ae-c54c94fd525b: alive
    https://storage2:60006/Shepherd 97edebb5-e72d-098a-55a7-14595f668770: alive
[...]    
\end{verbatim}

@@

ARC has its own multi-protocol storage client tools which provide a unified way to access different kind of storage. For all the supported types there is a DMC module. We created a DMC module for the ARC storage as well. If it is compiled and installed, then you can use the \verb!arcls!, \verb!arccp!, \verb!arcrm!, etc. tools with the \verb!arc://! protocol to access the ARC storage system. You need to have a Bartender URL configured in the \verb!client.xml! user config.

\begin{verbatim}
$ arcls arc:///
$ arccp orange arc:///orange
$ arcls arc:///
orange
$ arccp arc:///orange /tmp/orange
$ cat /tmp/orange 
orange
$ arcrm arc:///orange
$ arcls arc:///
$ 
\end{verbatim}

TODO: if Bartender returns a ByteIO URL - not good, need to fix it.

>>>>

\begin{verbatim}
$ arc_storage_cli makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.81 seconds.
Creating collection '/': done

@@

\begin{verbatim}
$ arc_storage_cli makeCollection /fruits
- Calling the Bartender's makeCollection method...
- done in 0.79 seconds.
Creating collection '/fruits': done

$ arc_storage_cli makeCollecion /fruits/apple
- Calling the Bartender's makeCollection method...
- done in 0.91 seconds.
Creating collection '/fruits/apple': done

@@

$ arc_storage_cli makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.63 seconds.
Creating collection '/': done

@@

With only one node of the replicated A-Hash the system is not ready to work, if we try to use it, we get an error message:
\begin{verbatim}
$ arc_storage_cli makeCollection /
- Calling the Bartender's makeCollection method...
- done in 0.55 seconds.
Creating collection '/': failed to create new librarian entry
\end{verbatim}

@@

\begin{verbatim}
$ arc_storage_cli makeCollection /
- Calling the Bartender's makeCollection method...
- done in 1.16 seconds.
Creating collection '/': done
$ arc_storage_cli put orange /
- The size of the file is 7 bytes
- Calculating md5 checksum...
- done in 0.0214 seconds, md5 checksum is 6aefd2842be62cd470709b27aedc7db7
- Calling the Bartender's putFile method...
- done in 2.22 seconds.
- Got transfer URL: http://storage:60001/hopi/3f903c50-0424-2891-5730-521cc00d96dc
- Uploading from 'orange'
    to 'http://storage:60001/hopi/3f903c50-0424-2891-5730-521cc00d96dc' with http...
    1 s:        0.0 kB       0.0 kB/s       0.0 kB/s    . . .       
- done in 1.0293 seconds.
'orange' (7 bytes) uploaded as '/orange'.
$ arc_storage_cli modify /orange set states neededReplicas 3
- Calling the Bartender's modify method...
- done in 0.74 seconds.
set
$ arc_storage_cli stat /orange
[...]
  locations
    https://storage:60000/Shepherd f4ad8530-354d-5066-04ae-c54c94fd525b: alive
[...]
zsombor@storage:~$ arc_storage_cli stat /orange
[...]
  locations
    https://storage:60000/Shepherd f4ad8530-354d-5066-04ae-c54c94fd525b: alive
    https://storage2:60006/Shepherd 97edebb5-e72d-098a-55a7-14595f668770: alive
[...]    
\end{verbatim}

@@

ARC has its own multi-protocol storage client tools which provide a unified way to access different kind of storage. For all the supported types there is a DMC module. We created a DMC module for the ARC storage as well. If it is compiled and installed, then you can use the \verb!arcls!, \verb!arccp!, \verb!arcrm!, etc. tools with the \verb!arc://! protocol to access the ARC storage system. You can specify the URL of the Bartender with the \verb!BartenderURL! URL option, or you can have a Bartender URL configured in the \verb!client.xml! user config.

\begin{verbatim}
$ arcls arc:///
$ arccp orange arc:///orange
$ arcls arc:///
orange
$ arcls arc:///?BartenderURL=https://storage2:60006/Bartender
orange
$ arc_storage_cli list /
- Calling the Bartender's list method...
- done in 0.56 seconds.
'/': collection
  orange <file>
$ arc_storage_cli makeCollection /fruits
- Calling the Bartender's makeCollection method...
- done in 2.38 seconds.
Creating collection '/fruits': done
$ arccp arc:///orange arc:///fruits/orange
$ arcls arc:///
orange
fruits
$ arcls arc:///fruits
orange
$ arccp arc:///orange /tmp/orange
$ cat /tmp/orange 
orange
$ arcrm arc:///orange
$ arcls arc:///
fruits
\end{verbatim}
